---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# coauthornetwork

The goal of coauthornetwork is to plot a network of authors-coauthors from Google Scholar.

## Installation

You can install it from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cimentadaj/coauthornetwork")
```
## Example

The package only has two functions: `grab_network` to extract the network of coauthors and `plot_coauthors` to plot the network as a `ggraph`. The only thing you need is the string in the Google Scholar profile after the root of the website. For example, a Google Scholar profile URL is typically structured like this `https://scholar.google.es/citations?user=wKNoabEAAAAJ&hl=en&oi=ao`. `grab_network` will accept the end of the URL: `citations?user=wKNoabEAAAAJ&hl=en&oi=ao` and search for the network of coauthors.

A basic example:

```{r example}
library(coauthornetwork)

final_network <- grab_network('citations?user=wKNoabEAAAAJ&hl=en&oi=ao')
plot_coauthors(final_network)
```

`grab_network` has an additional argument called `n_deep` which controls the degree of depth in which to go down the coauthorship list. An `n_deep` of 1 (default) will grab all of the coauthors of the Google Scholar profile and also their coauthors. An `n_deep` of 2 will expand to this:

Google Scholar Profile -- > Coauthors --> Coauthors --> Coauthors

I urge the user to use an `n_deep` of 2 at most because the network can grow exponentially with an `n_deep` of 2 or above. For example..

```{r pressure, echo = FALSE}
final_network <- grab_network('citations?user=wKNoabEAAAAJ&hl=en&oi=ao', n_deep = 2)
plot_coauthors(final_network)
```
